---
title: "Thesis - Data analysis"
author: "Eline Anslot"
date: "2023-08-09"
output: html_document
---

```{r loading libraries}
library(goldilocks)
library(ggplot2)
source("./Functions2.R")
```

# Dataset

```{r dataset}
load("./Dataset_lambda_0.3.RData")
data <- data_thesis
recruitment_acc <- recruitment_rate
```


```{r infor}
day_long <- 365 
day_short_later <- 180
day_short_before <- 30
outcome <- "mrs_365d_binary"

covariate_vec <- c("age", "ich_location", "ich_s_volume", "ivh_s_volume")
short_vec_later <- "mrs_180d_binary"
short_vec_before <- "mrs_30d_binary"

```


# Stage 1

## Proposed method short-term endpoint measured at day 30

### Descriptive
```{r cohorts short early}
#################################################
#######Sample at interim#######
#################################################
#time at which participants have completed the long-term endpoint y
time_ppt_long <- recruitment_acc + day_long

#Last participant considered at interim => index of that person
index_n1_ppt <- order(recruitment_acc)[design$n1]

#time at which the last n1 participant completed they long-term endpoint y
time_n1_ppt <- time_ppt_long[index_n1_ppt]

###Cohort1####
# Return true or false depending on whether participants have completed 
# the long-term endpoint at stage 1 
indices_long <- time_ppt_long <= time_n1_ppt & 
  1:length(recruitment_acc) %in% order(recruitment_acc)[1:design$n1]

#Subgroup of the sample at interim which have all information 
#(baseline covariates, short_term and long-term endpoints)
cohort1_l <- data[indices_long, ]

#The baseline covariates that we will take into account
cohort_cov_var <- covariate_vec

#time at which participants have completed the short-term endpoint x
time_ppt_short <- recruitment_acc + day_short_before

# Return true or false depending on whether we have
# information on the short-term endpoint at stage 1 
indices_short <- time_ppt_short <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates at stage 1 
indices_bascov <- recruitment_acc <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates and short term but not
# of the long term endpoint at stage 1 ==> Cohort 2
indices_cohort2 <- indices_short &! indices_long

# Return true or false depending on whether we have
# information on the baseline covariates but not on the short-term and 
# on the long term endpoint at stage 1 => Cohort 3
indices_cohort3 <- indices_bascov &! indices_short

#The baseline covariates and short term endpoint variables that we will take
#into account
cohort_short_var <- c(covariate_vec, short_vec_before)

#####Subgroups######
###Cohort2####
#Participants with baseline covariates and short-term endpoint but no 
#long-term endpoint
cohort2_s <- data[indices_cohort2, cohort_short_var, drop = FALSE]

###Cohort3###
#Participants with only baseline covariates information
cohort3_bc     <- data[indices_cohort3, cohort_cov_var, drop = FALSE]
```

#### Cohort 1 
```{r des short early}
print("age")
mean(cohort1_l$age)
sd(cohort1_l$age)
cor(cohort1_l$age, cohort1_l$mrs_365d_binary)

print("gender")
table(cohort1_l$male)

print("ich_location")
table(cohort1_l$ich_location)
cor(cohort1_l$ich_s_volume, cohort1_l$mrs_365d_binary)

print("ich_s_volume")
mean(cohort1_l$ich_s_volume)
sd(cohort1_l$ich_s_volume)
cor(as.numeric(cohort1_l$ich_location == "Deep"), cohort1_l$mrs_365d_binary)

print("ivh_s_volume")
mean(cohort1_l$ivh_s_volume)
sd(cohort1_l$ivh_s_volume)
cor(cohort1_l$ivh_s_volume, cohort1_l$mrs_365d_binary)

print("X30d")
table(cohort1_l$mrs_30d_binary)
table(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)

print("X180d")
table(cohort1_l$mrs_180d_binary)
table(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)

print("X365d")
table(cohort1_l$mrs_365d_binary)
```

#### Cohort 3 
```{r des cohort 3 X30}
print("age")
mean(cohort2_s$age)
sd(cohort2_s$age)

print("ich_location")
table(cohort2_s$ich_location)

print("ich_s_volume")
mean(cohort2_s$ich_s_volume)
sd(cohort2_s$ich_s_volume)

print("ivh_s_volume")
mean(cohort2_s$ivh_s_volume)
sd(cohort2_s$ivh_s_volume)

print("X30d")
table(cohort2_s$mrs_30d_binary)
```
```{r explorative }
cor(data[indices_cohort2, c("mrs_30d_binary", "mrs_365d_binary")])
```

### Analyses

```{r analysis method short early}
#################################################
#######Estimate#######
#################################################
model   <- glm(to_formula(outcome, cohort_short_var),
               family = binomial(link = "logit"),
               data = cohort1_l)

data_cohort1_2 <- rbind(cohort1_l[, cohort_short_var, drop = FALSE], 
                        cohort2_s)

predict2 <- predict(model, 
                    type = "response",
                    newdata = data_cohort1_2)

model2 <- glm(to_formula("predict2", cohort_cov_var),
              family = binomial(link="logit"),
              data = cbind(data_cohort1_2, predict2))

predict <- predict(model2,
                   type = "response",
                   newdata = rbind(data_cohort1_2[, cohort_cov_var, drop = FALSE],
                                   cohort3_bc))

estimate <- mean(predict)

#################################################
#######Variance#######
#################################################
new_indices_long <- indices_long[indices_bascov]
new_indices_short <- indices_short[indices_bascov]
cycx <- new_indices_long/(mean(new_indices_long))#*mean(new_indices_short))
predict2_adj <- c(predict2, rep(0, times = sum(indices_bascov) - length(predict2)))
yi_yihat <- data[indices_bascov, outcome] - predict2_adj
predict_adj <- c(predict, rep(0, times = sum(indices_bascov) - length(predict)))
cix_yihat_yihat2 <- (new_indices_short/mean(new_indices_short) ) *(predict2_adj - predict_adj)
variance <- var( (cycx*yi_yihat + cix_yihat_yihat2 + predict_adj) )

#################################################
#######Results#######
#################################################

results <- list(estimate = estimate,
                variance = variance,
                n_cohort1 = sum(indices_long),
                n_cohort2 = sum(indices_cohort2),
                n_cohort3 = sum(indices_cohort3),
                n_interim = sum(indices_cohort2) + 
                            sum(indices_cohort3) + 
                            sum(indices_long))
results
```

```{r decisions early}
##Suggested method##
se <- sqrt(results$variance/results$n_interim)
t1 <- (results$estimate - design$p0)/se
VL_decision <- ifelse(t1 <= qnorm(design$PET), "stop", "continue")
```


## Proposed method short-term endpoint measured at day 180
### Descriptive
```{r cohort shorts late}
#################################################
#######Sample at interim#######
#################################################
#time at which participants have completed the long-term endpoint y
time_ppt_long <- recruitment_acc + day_long

#Last participant considered at interim => index of that person
index_n1_ppt <- order(recruitment_acc)[design$n1]

#time at which the last n1 participant completed they long-term endpoint y
time_n1_ppt <- time_ppt_long[index_n1_ppt]

###Cohort1####
# Return true or false depending on whether participants have completed 
# the long-term endpoint at stage 1 
indices_long <- time_ppt_long <= time_n1_ppt & 
  1:length(recruitment_acc) %in% order(recruitment_acc)[1:design$n1]

#Subgroup of the sample at interim which have all information 
#(baseline covariates, short_term and long-term endpoints)
cohort1_l <- data[indices_long, ]

#The baseline covariates that we will take into account
cohort_cov_var <- covariate_vec

#time at which participants have completed the short-term endpoint x
time_ppt_short <- recruitment_acc + day_short_later

# Return true or false depending on whether we have
# information on the short-term endpoint at stage 1 
indices_short <- time_ppt_short <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates at stage 1 
indices_bascov <- recruitment_acc <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates and short term but not
# of the long term endpoint at stage 1 ==> Cohort 2
indices_cohort2 <- indices_short &! indices_long

# Return true or false depending on whether we have
# information on the baseline covariates but not on the short-term and 
# on the long term endpoint at stage 1 => Cohort 3
indices_cohort3 <- indices_bascov &! indices_short

#The baseline covariates and short term endpoint variables that we will take
#into account
cohort_short_var <- c(covariate_vec, short_vec_later)

#####Subgroups######
###Cohort2####
#Participants with baseline covariates and short-term endpoint but no 
#long-term endpoint
cohort2_s <- data[indices_cohort2, cohort_short_var, drop = FALSE]

###Cohort3###
#Participants with only baseline covariates information
cohort3_bc     <- data[indices_cohort3, cohort_cov_var, drop = FALSE]
```


#### Cohort 1 
```{r des short late}
print("age")
mean(cohort1_l$age)
sd(cohort1_l$age)
cor(cohort1_l$age, cohort1_l$mrs_365d_binary)

print("gender")
table(cohort1_l$male)

print("ich_location")
table(cohort1_l$ich_location)
cor(cohort1_l$ich_s_volume, cohort1_l$mrs_365d_binary)

print("ich_s_volume")
mean(cohort1_l$ich_s_volume)
sd(cohort1_l$ich_s_volume)
cor(as.numeric(cohort1_l$ich_location == "Deep"), cohort1_l$mrs_365d_binary)

print("ivh_s_volume")
mean(cohort1_l$ivh_s_volume)
sd(cohort1_l$ivh_s_volume)
cor(cohort1_l$ivh_s_volume, cohort1_l$mrs_365d_binary)

print("X30d")
table(cohort1_l$mrs_30d_binary)
table(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)

print("X180d")
table(cohort1_l$mrs_180d_binary)
table(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)

print("X365d")
table(cohort1_l$mrs_365d_binary)
```

#### Cohort 2
```{r des cohort 2 X180}
print("age")
mean(cohort2_s$age)
sd(cohort2_s$age)

print("ich_location")
table(cohort2_s$ich_location)

print("ich_s_volume")
mean(cohort2_s$ich_s_volume)
sd(cohort2_s$ich_s_volume)

print("ivh_s_volume")
mean(cohort2_s$ivh_s_volume)
sd(cohort2_s$ivh_s_volume)

print("X180d")
table(cohort2_s$mrs_180d_binary)
```
#### Cohort 4
```{r des cohort 4 X180}
print("age")
mean(cohort3_bc$age)
sd(cohort3_bc$age)

print("ich_location")
table(cohort3_bc$ich_location)

print("ich_s_volume")
mean(cohort3_bc$ich_s_volume)
sd(cohort3_bc$ich_s_volume)

print("ivh_s_volume")
mean(cohort3_bc$ivh_s_volume)
sd(cohort3_bc$ivh_s_volume)
```


### Analysis
```{r analysis short later}
#################################################
#######Estimate#######
#################################################
model   <- glm(to_formula(outcome, cohort_short_var),
               family = binomial(link = "logit"),
               data = cohort1_l)

data_cohort1_2 <- rbind(cohort1_l[, cohort_short_var, drop = FALSE], 
                        cohort2_s)

predict2 <- predict(model, 
                    type = "response",
                    newdata = data_cohort1_2)

model2 <- glm(to_formula("predict2", cohort_cov_var),
              family = binomial(link="logit"),
              data = cbind(data_cohort1_2, predict2))

predict <- predict(model2,
                   type = "response",
                   newdata = rbind(data_cohort1_2[, cohort_cov_var, drop = FALSE],
                                   cohort3_bc))

estimate <- mean(predict)

#################################################
#######Variance#######
#################################################
new_indices_long <- indices_long[indices_bascov]
new_indices_short <- indices_short[indices_bascov]
cycx <- new_indices_long/(mean(new_indices_long))#*mean(new_indices_short))
predict2_adj <- c(predict2, rep(0, times = sum(indices_bascov) - length(predict2)))
yi_yihat <- data[indices_bascov, outcome] - predict2_adj
predict_adj <- c(predict, rep(0, times = sum(indices_bascov) - length(predict)))
cix_yihat_yihat2 <- (new_indices_short/mean(new_indices_short) ) *(predict2_adj - predict_adj)
variance <- var( (cycx*yi_yihat + cix_yihat_yihat2 + predict_adj) )

#################################################
#######Results#######
#################################################

results <- list(estimate = estimate,
                variance = variance,
                n_cohort1 = sum(indices_long),
                n_cohort2 = sum(indices_cohort2),
                n_cohort3 = sum(indices_cohort3),
                n_interim = sum(indices_cohort2) + 
                            sum(indices_cohort3) + 
                            sum(indices_long))
results
```

```{r decisions short later}
##Suggested method##
se <- sqrt(results$variance/results$n_interim)
t1 <- (results$estimate - design$p0)/se
VL_decision <- ifelse(t1 <= qnorm(design$PET), "stop", "continue")
```

## Proposed method both short-term endpoints
### Descriptive
```{r cohorts both shorts}
#################################################
#######Sample at interim#######
#################################################
#time at which participants have completed the long-term endpoint y
time_ppt_long <- recruitment_acc + day_long

#Last participant considered at interim => index of that person
index_n1_ppt <- order(recruitment_acc)[design$n1]

#time at which the last n1 participant completed they long-term endpoint y
time_n1_ppt <- time_ppt_long[index_n1_ppt]

###Cohort1####
# Return true or false depending on whether participants have completed 
# the long-term endpoint at stage 1 
indices_long <- time_ppt_long <= time_n1_ppt & 
  1:length(recruitment_acc) %in% order(recruitment_acc)[1:design$n1]

#Subgroup of the sample at interim which have all information 
#(baseline covariates, short_term and long-term endpoints)
cohort1_l <- data[indices_long, ]

#time at which participants have completed the short-term endpoint x
time_ppt_short_later <- recruitment_acc + day_short_later

# Return true or false depending on whether we have
# information on the short-term endpoint at stage 1 
indices_short_later <- time_ppt_short_later <= time_n1_ppt

#time at which participants have completed the short-term endpoint x
time_ppt_short_before <- recruitment_acc + day_short_before

# Return true or false depending on whether we have
# information on the short-term endpoint at stage 1 
indices_short_before <- time_ppt_short_before <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates at stage 1 
indices_bascov <- recruitment_acc <= time_n1_ppt

# Return true or false depending on whether we have
# information on the baseline covariates and short term but not
# of the long term endpoint at stage 1 ==> Cohort 2
indices_cohort2 <- indices_short_later &! indices_long

indices_cohort3 <- indices_short_before &! indices_short_later

# Return true or false depending on whether we have
# information on the baseline covariates but not on the short-term and 
# on the long term endpoint at stage 1 => Cohort 3
indices_cohort4 <- indices_bascov &! indices_short_before

#The baseline covariates and short term endpoint variables that we will take
#into account
cohort_short_later_var <- c(covariate_vec, "mrs_30d_binary", "mrs_180d_binary")
cohort_short_before_var <- c(covariate_vec, "mrs_30d_binary")
#The baseline covariates that we will take into account
cohort_cov_var <- covariate_vec
#####Subgroups######
###Cohort2####
#Participants with baseline covariates and short-term endpoint but no 
#long-term endpoint
cohort2_s <- data[indices_cohort2, cohort_short_later_var, drop = FALSE]

cohort3_s <- data[indices_cohort3, cohort_short_before_var, drop = FALSE]

###Cohort3###
#Participants with only baseline covariates information
cohort4_bc <- data[indices_cohort4, cohort_cov_var, drop = FALSE]
```


#### Cohort 1 
```{r des cohort 1}
print("age")
mean(cohort1_l$age)
sd(cohort1_l$age)
cor(cohort1_l$age, cohort1_l$mrs_365d_binary)

print("gender")
table(cohort1_l$male)

print("ich_location")
table(cohort1_l$ich_location)
cor(cohort1_l$ich_s_volume, cohort1_l$mrs_365d_binary)

print("ich_s_volume")
mean(cohort1_l$ich_s_volume)
sd(cohort1_l$ich_s_volume)
cor(as.numeric(cohort1_l$ich_location == "Deep"), cohort1_l$mrs_365d_binary)

print("ivh_s_volume")
mean(cohort1_l$ivh_s_volume)
sd(cohort1_l$ivh_s_volume)
cor(cohort1_l$ivh_s_volume, cohort1_l$mrs_365d_binary)

print("X30d")
table(cohort1_l$mrs_30d_binary)
table(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_30d_binary, cohort1_l$mrs_365d_binary)

print("X180d")
table(cohort1_l$mrs_180d_binary)
table(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)
cor(cohort1_l$mrs_180d_binary, cohort1_l$mrs_365d_binary)

print("X365d")
table(cohort1_l$mrs_365d_binary)
```

#### Cohort 2
```{r des cohort 2}
print("age")
mean(cohort2_s$age)
sd(cohort2_s$age)

print("ich_location")
table(cohort2_s$ich_location)

print("ich_s_volume")
mean(cohort2_s$ich_s_volume)
sd(cohort2_s$ich_s_volume)

print("ivh_s_volume")
mean(cohort2_s$ivh_s_volume)
sd(cohort2_s$ivh_s_volume)

print("X180d")
table(cohort2_s$mrs_180d_binary)
```
#### Cohort 3
```{r des cohort3}
print("age")
mean(cohort3_s$age)
sd(cohort3_s$age)

print("ich_location")
table(cohort3_s$ich_location)

print("ich_s_volume")
mean(cohort3_s$ich_s_volume)
sd(cohort3_s$ich_s_volume)

print("ivh_s_volume")
mean(cohort3_s$ivh_s_volume)
sd(cohort3_s$ivh_s_volume)

print("X30")
table(cohort3_s$mrs_30d_binary)
```

```{r explorative both }
cor(data[indices_cohort3, c("mrs_30d_binary", "mrs_365d_binary")])
cor(data[indices_cohort2, c("mrs_30d_binary", "mrs_180d_binary", "mrs_365d_binary")])
```

### Analysis
```{r analysis with both shorts}
#################################################
#######Estimate####### 
#################################################
model   <- glm(to_formula(outcome, cohort_short_later_var),
               family = binomial(link = "logit"),
               data = cohort1_l)

data_cohort1_2 <- rbind(cohort1_l[, cohort_short_later_var, drop = FALSE], 
                        cohort2_s)

predict2 <- predict(model, 
                    type = "response",
                    newdata = data_cohort1_2)

model2 <- glm(to_formula("predict2", cohort_short_before_var),
              family = binomial(link="logit"),
              data = cbind(data_cohort1_2, predict2))

data_cohort1_2_3 <- rbind(data_cohort1_2[, cohort_short_before_var, drop = FALSE],
                                   cohort3_s)

predict3 <- predict(model2,
                   type = "response",
                   newdata = data_cohort1_2_3)

model3 <- glm(to_formula("predict3", cohort_cov_var),
              family = binomial(link="logit"),
              data = cbind(data_cohort1_2_3, predict3))

predict <- predict(model3,
                   type = "response",
                   newdata = c(data_cohort1_2_3,
                                   cohort4_bc))

estimate <- mean(predict)

#################################################
#######Variance#######
#################################################

new_indices_long         <- indices_long[indices_bascov]
new_indices_short_later  <- indices_short_later[indices_bascov]
new_indices_short_before <- indices_short_before[indices_bascov]

#Probability to havve a long-term endpoint Y=> n_cohort1/n_interim:
#mean(indices_long[indices_short_later])*mean(indices_short_later[indices_short_before])*mean(indices_short_before[indices_bascov]) = mean(new_indices_long) => Binary_index/prob_Y
#=> scale term for those who have a long-term endpoint Y
prob_Y <- new_indices_long/mean(new_indices_long)

#Probability to have a short-term endpoint later
prob_X_later <- new_indices_short_later/mean(new_indices_short_later)

#Probability to have a short-term endpoint before
prob_X_before <- new_indices_short_before/mean(new_indices_short_before)

predict2 <- c(predict2, rep(0, times = sum(indices_bascov) - length(predict2)))
error_prediction2 <- data[indices_bascov, outcome] - predict2

predict3 <- c(predict3, rep(0, times = sum(indices_bascov) - length(predict3)))
error_prediction3 <- predict2 - predict3

predict <- c(predict, rep(0, times = sum(indices_bascov) - length(predict)))
error_prediction <- predict3 - predict

variance <- var(prob_Y*error_prediction2 + prob_X_later*error_prediction3 + prob_X_before*error_prediction + predict)

#################################################
#######Results#######
#################################################

results <- list(estimate = estimate,
                variance = variance,
                n_cohort1 = sum(indices_long),
                n_cohort2 = sum(indices_cohort2),
                n_cohort3 = sum(indices_cohort3),
                n_cohort4 = sum(indices_cohort4),
                n_interim = sum(indices_cohort2) + 
                            sum(indices_cohort3) + 
                            sum(indices_long) +
                            sum(indices_cohort4))
results
```

```{r decisions short both}
##Suggested method##
se <- sqrt(results$variance/results$n_interim)
t1 <- (results$estimate - design$p0)/se
VL_decision <- ifelse(t1 <= qnorm(design$PET), "stop", "continue")
```

# Stage 2
## Descriptive
### Gender
```{r gender}
n_male <-sum(data$male)
```

### Age
```{r age stage 2}
data.frame(cat = c("all", "man", "women"),
           mean = c(mean(data$age), mean(data$age[data$male == 1]), mean(data$age[data$male == 0])),
           sd = c(sd(data$age), sd(data$age[data$male == 1]), sd(data$age[data$male == 0])),
           max = c(max(data$age), max(data$age[data$male == 1]), max(data$age[data$male == 0])),
           min = c(min(data$age), min(data$age[data$male == 1]), min(data$age[data$male == 0]))
)

hist(data$age)
hist(data$age[data$male == 1])
hist(data$age[data$male == 0])

cor(data$age, data$mrs_365d_binary)

ggplot(data = data, mapping = aes(x = factor(mrs_365d_binary), y = age)) +
  geom_boxplot() + 
  ylab("Age (years)") +
  scale_x_discrete(name ="Functional outcome at day 365", 
                  labels= c("0" = "Failure", "1" = "Success"))
```
### Ich_location

```{r ich_location stage 2}
sum(data$ich_location == "Deep")
sum(data$ich_location == "Lobar")
table(data$ich_location, data$mrs_365d_binary)
cor(as.numeric(data$ich_location == "Deep"), data$mrs_365d_binary)
```
### Ich_s_volume
```{r ich_volume stage 2}
mean(data$ich_s_volume)
sd(data$ich_s_volume)
min(data$ich_s_volume)
max(data$ich_s_volume)
quantile(data$ich_s_volume, probs = c(0.25, 0.75))

ggplot(data = data, mapping = aes(x = factor(mrs_365d_binary), y = ich_s_volume)) +
  geom_boxplot() + 
  scale_x_discrete(name ="Functional outcome at day 365", 
                  labels= c("0" = "Failure", "1" = "Success"))

cor(data$ich_s_volume, data$mrs_365d_binary)
```


### Ivh_s_volume
```{r ivh_volume stage 2}
mean(data$ivh_s_volume)
sd(data$ivh_s_volume)
min(data$ivh_s_volume)
max(data$ivh_s_volume)
quantile(data$ivh_s_volume, probs = c(0.25, 0.75))

ggplot(data = data, mapping = aes(x = factor(mrs_365d_binary), y = ivh_s_volume)) +
  geom_boxplot() + 
  scale_x_discrete(name ="Functional outcome at day 365", 
                  labels= c("0" = "Failure", "1" = "Success"))
plot(data$mrs_365d_binary, data$ivh_s_volume)
table(data$mrs_365d_binary, data$ivh_s_volume)

cor(data$ivh_s_volume, data$mrs_365d_binary)
```

### X30d
```{r X30d}
sum(data$mrs_30d_binary == "0")
sum(data$mrs_30d_binary == "1")
table(data$mrs_30d_binary, data$mrs_365d_binary)
cor(data$mrs_30d_binary, data$mrs_365d_binary)
```
### X180d
```{r X180d}
sum(data$mrs_180d_binary == "0")
sum(data$mrs_180d_binary == "1")
table(data$mrs_180d_binary, data$mrs_365d_binary)
cor(data$mrs_180d_binary, data$mrs_365d_binary)
```

## Analyse
```{r decision stage 2}
decision_stage2(data$mrs_365d_binary, design$r2)
```

